---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# obcogen

<!-- badges: start -->
<!-- badges: end -->

The goal of obcogen is to ...

## Installation

You can install the development version of obcogen from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("paulinone/obcogen")
```

## Example

Imagine you want to test that first six rows of the iris dataset equal the following.
```{r}
hr <- head(iris)
hr
```


Now you could type out `hr1 <- data.frame(Sepal.Length = c(5.1, 4.9, 4.7, 4.6, 5.0, 5.4), Sepal.Width = c(3.5, 3.0, 3.2, 3.1, 3.6, 3.9), Petal.Length = c(1.4, 1.4, 1.3, 1.5, 1.4, 1.7), Petal.Width = c(0.2, 0.2, 0.2, 0.2, 0.2, 0.4), Species = c("setosa", "setosa", "setosa", "setosa", "setosa", "setosa"))`. But what if you forget to type a `c` or a `,`  or forgot an `'s'` in `'setosa`. (All of these may or may have happen while writing out this short example). Your object would not be the same. Then the code would break and frankly I would rather not waste time doing this. This example is 6 rows, but what if you were doing the whole `iris` dataset. 
 
```{r example}
library(obcogen)
code_gen(hr)
```

```{r}
## The code I wrote above
hr1 <- data.frame(Sepal.Length = c(5.1, 4.9, 4.7, 4.6, 5.0, 5.4), Sepal.Width = c(3.5, 3.0, 3.2, 3.1, 3.6, 3.9), Petal.Length = c(1.4, 1.4, 1.3, 1.5, 1.4, 1.7), Petal.Width = c(0.2, 0.2, 0.2, 0.2, 0.2, 0.4), Species = c("setosa", "setosa", "setosa", "setosa", "setosa", "setosa"))

## The code generated that was copy and pasted
hr2 <- data.frame(Sepal.Length = as.numeric(c(5.1, 4.9, 4.7, 4.6, 5, 5.4)), Sepal.Width = as.numeric(c(3.5, 3, 3.2, 3.1, 3.6, 3.9)), Petal.Length = as.numeric(c(1.4, 1.4, 1.3, 1.5, 1.4, 1.7)), Petal.Width = as.numeric(c(0.2, 0.2, 0.2, 0.2, 0.2, 0.4)), Species = factor(c('setosa', 'setosa', 'setosa', 'setosa', 'setosa', 'setosa'), levels = c('setosa', 'versicolor', 'virginica')))

waldo::compare(hr, hr1)
waldo::compare(hr, hr2)

```

I failed to realize that species was a factor and hr and hr1 were not the same, but hr and hr are the same.
 
And just a final comparison, with both waldo and testthat
```{r}
## this should not work
try(testthat::expect_equal(head(iris), hr1))

waldo::compare(head(iris), hr2)
testthat::expect_equal(head(iris), hr2)

```

It works! They are infact identical. 
.
