---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# obcogen

<!-- badges: start -->
<!-- badges: end -->

The goal of obcogen is to ...

## Installation

You can install the development version of obcogen from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("paulinone/obcogen")
```

## Example

Imagine you want to test that first six rows of the iris dataset equal the following.
```{r}
hr <- head(iris)
hr
```


Now you could type out hr1 <- data.frame(Sepal.Length = c(5.1, 4.9, 4.7, 4.6, 5.0, 5.4), Sepal.Width = c(3.5, 3.0, 3.2, 3.1, 3.6, 3.9), Petal.Length = c(1.4, 1.4, 1.3, 1.5, 1.4. 1.7), Petal.Width = c(0.2, 0.2, 0.2 0.2, 0.2, 0.4), Species = c("setosa", "setosa", "setosa", "setosa", "setosa", "setosa")). But what if you forget to type a 'c' or a ',' or forgot an 's' in 'setosa'. (All of these may or may have happen while writting out this short example). Your object would not be the same. Then the code would break and frankly I would rather not waste time doing this. 
 
```{r example}
library(obcogen)
gen_code(hr)
```



```{r cars}
summary(cars)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

.
